---
title: "Shiny Application Pitch"
author: "Darrr"
date: "February 1, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE, fig.align="center"}
knitr::opts_chunk$set(echo = FALSE)
```

## The purpose 

* Do you ever wanted to know your destiny?

* Are you struggling from partners that doesn`t fit you?

* Do you ever wanted to have no responsibility for your actions?

I have a simple answer for you

(c)further information is just for fun

***


Just  use this delightful application for finding out your zodiac sign.
And do whatever the horoscope tells*



*please, dont do it. 

##Some embedded R code that gets run when slidifying the document

```{r echo=FALSE}
sc<-seq(1,20)
rh<-seq(1,20)
plot(rh,sc,type="l",main="Amount of succes vs. Reading horoscopes", xlab="Times reading horoscope per day", ylab="Number of succesful decicions per month")
```

## How it works

* Select your month of birth

* Select your date og birth

* Get your zodiac sign


## Ready

You are marvelous!

